---
title: "datasauRus"
author: "Kasia Banas"
date: "2024-09-26"
output: html_document
---

Install and load the datasauRus library:

```{r}
# install.packages("datasauRus")
library(datasauRus)
```

Load the tidyverse: 
```{r}
library(tidyverse)
```

`datasaurus_dozen` is a dataset demonstrating the utility of visualization. 
These 12 datasets are equal in standard measures: mean, standard deviation, 
and Pearson's correlation. But they look very different
Run the chunk below to get more info about this dataset:

```{r}
?datasaurus_dozen
```

See what datasets are in the datasaurus_dozen:

```{r}
datasaurus_dozen %>% 
  distinct(dataset)
```

## Exercise 1
Pick 2 datasets and plot them next to one another
(I'd recommend scatterplot, use facets if you like)

```{r}
datasaurus_dozen %>% 
  filter(dataset %in% c('dino', 'slant_up')) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + facet_wrap(~ dataset)

```

## Exercise 2
For these same two datasets, find the mean and standard deviation
for the x and y variable in each. What did you find? 

```{r}
datasaurus_dozen %>% 
  filter(dataset %in% c('dino', 'slant_up')) %>% 
  group_by(dataset) %>% 
  summarise(mean_x_value = mean(x), sd_x = sd(x), mean_y_value = mean(y), sd_y = sd(y))
```
